Reducing Acceptance Marks in Emerson-Lei Automata by QBF-solving

### 2022-04-26 paper/main.tex
HW info

Spot version 2.10.4 and Z3 version 4.8.13 have been used in the
experimental evaluation. The experiments have been run on a computer
with Intel® Core™ i7-8550U processor and 16 GB of memory running
Debian 11.

>>>>

Spot version 2.10.3.dev and Z3 version 4.8.15 have been used in the
experimental evaluation. The experiments have been run on a computer
with Intel® Core™ i7-8700 processor and 32 GB of memory running
Ubuntu 20.04.4.
